\section{Introduction}
\label{sec:intro}

Dense 3D maps are essential for navigation, manipulation, and scene understanding in robotics and augmented reality. Volumetric fusion methods~\cite{10.1145/3596711.3596726,newcombe2011kinectfusion} represent the scene as a Truncated Signed Distance Field (TSDF) and integrate depth measurements incrementally, producing high-quality surfaces even under sensor noise. Real-time implementations based on spatial hashing~\cite{10.1145/2508363.2508374} and efficient data structures~\cite{Oleynikova_2017,vizzo2022vdbfusion} have made volumetric mapping practical for large-scale deployment on mobile robots, autonomous vehicles, and MAVs.

These systems consume camera poses from an external SLAM front-end and fuse depth observations, but take no responsibility for correcting pose errors. This creates a fundamental incompatibility with modern SLAM systems~\cite{Campos_2021} that perform \emph{loop closure}: when the back-end detects a revisited location, pose-graph optimization~\cite{5979949} retroactively corrects the entire trajectory to eliminate accumulated drift. The volumetric map, built with the pre-correction (drifted) poses, becomes geometrically inconsistent with the corrected trajectory (Fig.~\ref{fig:teaser}).

\vspace{1mm}\noindent\textit{The map rebuild bottleneck.}
The standard remedy is to discard the map and reintegrate all $N$ depth frames with corrected poses\cite{Cramariuc_2023,rosinol2021kimeraslamspatialperception}. The complexity is $O(N \cdot |\Omega|)$, where $|\Omega|$ is the image resolution -- for sessions of thousands of frames this takes minutes on high-end hardware. Worse, it must repeat after \emph{every} loop closure, making tightly-coupled SLAM-plus-mapping pipelines impractical for large-scale or multi-session deployments.

\vspace{1mm}\noindent\textit{Why existing solutions fall short.}
Submap-based methods such as Voxgraph~\cite{reijgwart2020voxgraph} and FlashFusion~\cite{han2018flashfusion} apply rigid per-submap transforms but leave intra-submap drift uncorrected. Non-rigid surfel SLAM~\cite{whelan2016elasticfusion} is self-contained and not designed for external pose-graph corrections. Neural implicit approaches~\cite{sucar2021imap,zhu2022niceslam,liso2024loopyslam,bruns2024neuralgraphmap} either lack loop closure or require expensive re-optimization.

\vspace{1mm}\noindent\textit{Observation invariance: the key insight.}
We identify a property that makes the problem tractable: a calibrated surface sample expressed in its sensor frame is unchanged by a later world-frame pose correction. During streaming fusion, WarpVox retains a bounded set of such samples together with their acquisition timestamps and surface support. Re-expressing the same samples with corrected poses yields corrected world-space targets. Loop correction therefore consumes bounded records rather than the historical depth stream.

\vspace{1mm}\noindent\textit{Our approach.}
We propose \emph{WarpVox}, a four-stage pipeline that exploits this invariance to update a TSDF after loop closure without reintegration. We (i)~associate bounded sensor-frame evidence with the pre-correction surface, (ii)~use the corrected poses and these associations to compute robust surface targets, (iii)~propagate sparse displacements through one ARAP deformation~\cite{ARAP_modeling:2007} on a QEM surface proxy, and (iv)~reconstruct a TSDF whose zero set follows the warped surface while its support and confidence follow the source volume. Once records are maintained by the streaming mapper, correction scales with active surface and volume, not with the number of accumulated frames.

\vspace{1mm}\noindent\textit{Contributions.}
\begin{itemize}
    \item We formulate loop-closure map correction from bounded vertex--observation associations, decoupling correction from accumulated raw frames.
    \item We combine observation-derived targets, one proxy ARAP solve, and source-supported TSDF reconstruction to return a standard volume suitable for continued fusion.
    \item We evaluate against full reintegration and mapping baselines over 51 checkpoints, separately compare final-state correction with Kimera-PGMO over ten complete Kimera-Multi bags, and extend the target mechanism to Gaussian primitives.
\end{itemize}