\section{Related Work}
\label{sec:related}

\vspace{1mm}\noindent\textit{Volumetric SLAM and dense mapping.}
The seminal work of Curless and Levoy~\cite{10.1145/3596711.3596726} established TSDF integration as the standard paradigm for dense surface reconstruction from range data. KinectFusion~\cite{newcombe2011kinectfusion} demonstrated real-time volumetric fusion on GPU by coupling ICP-based tracking with TSDF integration into a fixed-size voxel grid. Spatial hashing~\cite{10.1145/2508363.2508374} extended this to unbounded scenes by allocating voxel blocks on demand. Voxblox~\cite{Oleynikova_2017} introduced an efficient incremental SDF mapping library designed for on-board deployment on MAVs, consuming poses from any external odometry source. VDBFusion~\cite{vizzo2022vdbfusion} provides a flexible alternative based on the OpenVDB hierarchical volume format. A common design assumption across all these systems is that the input trajectory is fixed; none provides a mechanism for updating the volumetric map when the trajectory is retroactively corrected by a pose-graph SLAM back-end.

\vspace{1mm}\noindent\textit{Loop closure in dense SLAM.}
Kintinuous~\cite{whelan2015kintinuous} addressed large-scale dense mapping by maintaining a sliding TSDF window and extracting point cloud slices as the camera moves; loop closure is handled by aligning cloud slices with a deformation graph, but only at the submap boundary level. ElasticFusion~\cite{whelan2016elasticfusion} represents the scene as a surfel map and performs frequent local non-rigid deformations using an embedded deformation graph, enabling real-time loop closure within its own tracking system. However, it is a self-contained SLAM system designed for room-scale environments, and its deformation mechanism is not directly applicable to an external TSDF receiving discrete pose-graph corrections. FlashFusion~\cite{han2018flashfusion} achieves real-time globally consistent reconstruction on CPU via rigid submaps and boundary reintegration. Voxgraph~\cite{reijgwart2020voxgraph} jointly optimizes a pose graph over SDF submaps, but likewise applies rigid per-submap corrections. WarpVox instead deforms an extracted surface with spatially varying targets and reconstructs a single corrected TSDF without decomposing the map into rigid submaps.

\vspace{1mm}\noindent\textit{Non-rigid deformation for 3D reconstruction.}
As-Rigid-As-Possible (ARAP) surface modeling~\cite{ARAP_modeling:2007} minimizes local rigidity distortion subject to positional constraints. Sumner \etal~\cite{10.1145/1276377.1276478} introduced embedded deformation graphs as sparse controls for arbitrary shapes. DynamicFusion~\cite{7298631}, KillingFusion~\cite{slavcheva2017killingfusion}, and VolumeDeform~\cite{innmann2016volumedeform} estimate non-rigid scene motion through continuous frame-to-frame tracking. Our setting instead receives a discrete trajectory correction for a static map. WarpVox uses the corrected poses and vertex--observation associations to compute surface targets, then propagates them with a single ARAP solve on a QEM proxy.

\vspace{1mm}\noindent\textit{Neural and Gaussian maps.}
iMAP~\cite{sucar2021imap}, NICE-SLAM~\cite{zhu2022niceslam}, and NGEL-SLAM~\cite{cui2023ngelslam} optimize neural scene representations, while Loopy-SLAM~\cite{liso2024loopyslam} couples loop closure to neural-map re-optimization. Neural Graph Map~\cite{bruns2024neuralgraphmap} instead anchors local fields to pose-graph nodes. Three-dimensional Gaussian splatting (3DGS) targets high-quality real-time rendering~\cite{kerbl2023gaussians}; SplaTAM~\cite{keetha2024splatam} uses differentiable rendering for dense RGB-D SLAM, and LoopSplat~\cite{zhu2025loopsplat} restores global consistency by rigidly aligning Gaussian submaps. These representations are effective for rendering, but they do not natively provide the signed-distance and observed-free-space structure used for obstacle-distance mapping. WarpVox primarily targets TSDF/ESDF robotics pipelines, while our geometry-only Gaussian experiment tests whether its observation-derived targets transfer beyond voxel grids.
